### 2012-03-27 exam4/2.tex
all java

\noindent\begin{minipage}{8cm}\sloppy
\begin{itemize}
\item You may use the usual primitives and expression forms of any of
  the \code{class} languages; for everything else, define it.

\item You may write {\tt {\slshape c} $\rightarrow$ {\slshape e}} as
  shorthand for writing both {\tt check-expect} and {\tt
    Tester.checkExpect}.

>>>>

\noindent\begin{minipage}{8cm}\sloppy
\begin{itemize}
\item All problems on this exam are in Java. You may use the the
  primitives and expression forms of Java, and the libraries we have
  used in class and in lab; anything else must be defined.

\item You may write {\tt {\slshape c} $\rightarrow$ {\slshape e}} as
  shorthand for writing {\tt
    Tester.checkExpect}; the {\tt Examples} class and {\tt test}
  method around the tests are not required.
